---
title: "CRPD Stream 1"
author: "Theodore Ochieng"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r Load Packages}
library(tidyverse)# Also loads dplyr, ggplot2, and haven
```

# Setup
```{r Function: countByGrouping}
countByGrouping <- function(dataset, varToGroup) {
  dataset %>% 
    count({{ varToGroup }}, sort = T) %>% 
    mutate(prop = round(n/sum(n), 4)) %>% 
    tibble() %>%
    return()
}
```


# Part 1: Load Data
```{r Load Data}
CRPD_StateReports <- read_csv("CRPD_Data/CRPD_StateReports_English_V2.csv")
combined_stopwords <- read_csv("CRPD_Data/combined_stopwords.csv")

head(CRPD_StateReports)
head(combined_stopwords)
```


```{r Records by Grouping}
countByGrouping(CRPD_StateReports, Year)
countByGrouping(CRPD_StateReports, Session)
countByGrouping(CRPD_StateReports, Country)
countByGrouping(CRPD_StateReports, Region)
countByGrouping(CRPD_StateReports, SubRegion)
countByGrouping(CRPD_StateReports, RegionalGroup)
countByGrouping(CRPD_StateReports, IncomeGroup)
```


```{r Check NAs}
# Get metadata about NAs 
CRPD_StateReports %>% 
  naniar::miss_var_summary() %>% 
  mutate(pct_miss = round(pct_miss, 2))
```


# Part 2: Keyword and Key-phrase Analysis
## Keywords
```{r Create Unigrams}
CRPD_StateReports_words <- 
  CRPD_StateReports %>%
  unnest_tokens(word, text) %>% 
  anti_join(combined_stopwords, by = "word")

tibble(CRPD_StateReports_words) %>%
  count(word, sort = T)

# Write to CSV
# tibble(CRPD_StateReports_words) %>%
#   count(word, sort = T) %>%
#   write_csv("CRPD_Meta/Metadata/unigram_counts_v2.csv")
```


```{r Plot - Frequent Words}
CRPD_StateReports_words %>%
  count(word, sort = TRUE) %>%
  slice_max(n, n = 25) %>% 
  mutate(word=reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col(alpha = 1, show.legend = FALSE, fill = "#4472C4") +
  coord_flip() +
  # geom_text(aes(label = scales::comma(n)),
  #           size = 3,
  #           vjust = 0.5,
  #           hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10)),
                     labels = scales::comma) +
  scale_x_reordered() +
  labs(x = NULL,
       y = "Frequency") +
  theme_bw() +
  theme(panel.grid.major.y = element_blank())

ggsave("CRPD_Data/Assets/freqUnigrams.jpg")
```


```{r TF-IDF Unigram}
unigram_tf_idf <- CRPD_StateReports_words %>%
  count(doc_id, word) %>% 
  bind_tf_idf(word, doc_id, n) %>%
  arrange(desc(tf_idf)) %>% 
  as_tibble()

unigram_tf_idf

unigram_tf_idf %>% 
  slice_max(n, n = 25) %>%  
  ggplot(aes(reorder(word,tf_idf), tf_idf)) + 
  geom_col(alpha = 1, show.legend = FALSE, fill = "#4472C4") +
  coord_flip() +
  # geom_text(aes(label = scales::comma(n)),
  #           size = 3,
  #           vjust = 0.5,
  #           hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10))) +
  scale_x_reordered() +
  labs(x = NULL,
       y = "TF-IDF") +
  theme_bw() +
  theme(panel.grid.major.y = element_blank())

ggsave("CRPD_Data/Assets/unigrams_TFIDF.jpg")

# Write CSV
# unigram_tf_idf %>%
#   write_csv("CRPD_Meta/Metadata/unigram_tf_idf.csv")
```


## Key Phrases
### Bigram
```{r Create Bigrams}
CRPD_StateReports_bigrams <- CRPD_StateReports %>%
  unnest_tokens(bigram, text, token = "ngrams", n=2)

CRPD_StateReports_bigrams %>%
  count(bigram, sort = TRUE) %>% 
  tibble() %>% 
  head(100)
```


```{r Bigrams Separated and Filtered}
# Runtime: 2mins
bigrams_filtered <- CRPD_StateReports_bigrams %>%
  filter(!grepl('[0-9]', bigram)) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>% 
  as_tibble() %>% 
  filter(!word1 %in% combined_stopwords$word) %>%
  filter(!word2 %in% combined_stopwords$word)

bigrams_filtered
```


```{r Bigrams Unite}
bigram_counts <- bigrams_filtered %>%
  count(word1, word2, sort = TRUE)

bigram_counts

bigrams_united <- bigrams_filtered %>%
  unite(bigram, word1, word2, sep = " ")

bigrams_united %>%
  as_tibble() %>% 
  count(bigram, sort = T)

# Write to CSV
# bigram_counts %>% 
#   write_csv("CRPD_Meta/Metadata/bigram_counts.csv")
```


```{r Plot - Bigram Frequency}
bigrams_united %>%
  count(bigram, sort = TRUE) %>% 
  mutate(bigram=reorder(bigram, n)) %>% 
  slice_max(n, n = 25) %>% 
  ggplot(aes(bigram,n)) +
  geom_col(alpha = 1, show.legend = FALSE, fill = "#4472C4") +
  coord_flip() +
  # geom_text(aes(label = scales::comma(n)),
  #           size = 3,
  #           vjust = 0.5,
  #           hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10)),
                     labels = scales::comma) +
  scale_x_reordered() +
  labs(x = NULL,
       y = "Frequency") +
  theme_bw() +
  theme(panel.grid.major.y = element_blank())

ggsave("CRPD_Data/Assets/freqBigrams.jpg")
```


```{r Check Word Precedents and Dependents}
bigrams_filtered %>%
  filter(word1 == "el") %>%
  count(word1, word2, sort = TRUE)

bigrams_filtered %>%
  filter(word2 == "el") %>%
  count(word1, word2, sort = TRUE)
```


```{r TF-IDF Bigram}
bigram_tf_idf <- bigrams_united %>%
  count(doc_id, bigram) %>%
  bind_tf_idf(bigram, doc_id, n) %>%
  arrange(desc(tf_idf))

bigram_tf_idf

bigram_tf_idf %>%
  slice_max(n, n = 25) %>% 
  ggplot(aes(reorder_within(bigram, tf_idf, tf_idf),tf_idf)) +
  geom_col(alpha = 1, show.legend = FALSE, fill = "#4472C4") +
  coord_flip() +
  # geom_text(aes(label = scales::comma(n)),
  #           size = 3,
  #           vjust = 0.5,
  #           hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10))) +
  scale_x_reordered() +
  labs(x = NULL,
       y = "TF-IDF") +
  theme_bw() +
  theme(panel.grid.major.y = element_blank())

ggsave("CRPD_Data/Assets/bigrams_TFIDF.jpg")

# Write CSV
# bigram_tf_idf %>%
#   write_csv("CRPD_Meta/Metadata/bigram_tf_idf.csv")
```


### Trigram
```{r Create Trigrams}
CRPD_StateReports_trigrams <- CRPD_StateReports %>%
  unnest_tokens(trigram, text, token = "ngrams", n=3)

CRPD_StateReports_trigrams %>%
  count(trigram, sort = TRUE) %>% 
  tibble() %>% 
  head(100)
```


```{r Trigrams Separated and Filtered}
# Runtime: 2m14s
trigrams_filtered <- CRPD_StateReports_trigrams %>%
  filter(!grepl('[0-9]', trigram)) %>%
  separate(trigram, c("word1", "word2", "word3"), sep = " ") %>% 
  as_tibble() %>% 
  filter(!word1 %in% combined_stopwords$word) %>%
  filter(!word2 %in% combined_stopwords$word) %>% 
  filter(!word3 %in% combined_stopwords$word)

trigrams_filtered
```


```{r Trigrams Unite}
trigram_counts <- trigrams_filtered %>%
  count(word1, word2, word3, sort = TRUE)

trigram_counts

trigrams_united <- trigrams_filtered %>%
  unite(trigram, word1, word2, word3, sep = " ")

trigrams_united %>%
  as_tibble() %>% 
  count(trigram, sort = T)

# Write to CSV
# trigram_counts %>%
#   write_csv("CRPD_Meta/Metadata/trigram_counts.csv")
```


```{r Plot - Trigram Frequency}
trigrams_united %>%
  count(trigram, sort = TRUE) %>% 
  mutate(trigram=reorder(trigram, n)) %>% 
  slice_max(n, n = 25) %>%
  ggplot(aes(trigram,n)) +
  geom_col(alpha = 1, show.legend = FALSE, fill = "#4472C4") +
  coord_flip() +
  # geom_text(aes(label = scales::comma(n)),
  #           size = 3,
  #           vjust = 0.5,
  #           hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10)),
                     labels = scales::comma) +
  scale_x_reordered() +
  labs(x = NULL,
       y = "Frequency") +
  theme_bw() +
  theme(panel.grid.major.y = element_blank())

ggsave("CRPD_Data/Assets/freqTrigrams.jpg")
```


```{r Check Word Precedents and Dependents}
trigrams_filtered %>%
  filter(word1 == "world") %>%
  count(word1, word2, word3, sort = TRUE)

trigrams_filtered %>%
  filter(word2 == "el") %>%
  count(word1, word2, word3, sort = TRUE)

trigrams_filtered %>%
  filter(word3 == "bank") %>%
  count(word1, word2, word3, sort = TRUE)
```


```{r TF-IDF Trigram}
trigram_tf_idf <- trigrams_united %>%
  count(doc_id, trigram) %>%
  bind_tf_idf(trigram, doc_id, n) %>%
  arrange(desc(tf_idf))

trigram_tf_idf

trigram_tf_idf %>%
  slice_max(n, n = 25) %>%
  ggplot(aes(reorder(trigram,tf_idf),tf_idf)) +
  geom_col(alpha = 1, show.legend = FALSE, fill = "#4472C4") +
  coord_flip() +
  # geom_text(aes(label = scales::comma(n)),
  #           size = 3,
  #           vjust = 0.5,
  #           hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10))) +
  scale_x_reordered() +
  labs(x = NULL,
       y = "TF-IDF") +
  theme_bw() +
  theme(panel.grid.major.y = element_blank())

ggsave("CRPD_Data/Assets/trigrams_TFIDF.jpg")

# Write CSV
# trigram_tf_idf %>%
#   write_csv("CRPD_Meta/Metadata/trigram_tf_idf.csv")
```



# Part 3: Dictionary Analysis
## Data Prep
```{r Load Packages}
library(quanteda)
library(tidytext)
```


```{r Create Corpus}
mycorpus <- corpus(CRPD_StateReports)

# corpus statistics for the first 10 observations
summary(mycorpus, 10)
```


```{r Remove Custom Stopwords}
stock_stopwords <- combined_stopwords %>% 
  filter(lexicon != "Custom_CRPD")

head(stock_stopwords)
```


```{r Create Tokens}
mytoken <-
  tokens(
    mycorpus,
    remove_numbers = TRUE,
    remove_punct = TRUE,
    remove_symbols = TRUE,
    remove_url = TRUE,
    split_hyphens = TRUE,
    include_docvars = TRUE
  )

mytoken<-tokens_tolower(mytoken)
mytoken<-tokens_remove(mytoken,stock_stopwords$word)

head(mytoken)
```


```{r Create DFM}
# Create Document-Feature Matrix (DFM)

# Without stemming
mydfm <- dfm(mytoken)
```


## Dictionary: CRPD
```{r Import Dictionary}
dict_CRPD <- readRDS("CRPD_Data/Dictionary/dict_CRPDFull_v2.rds")
```


### Apply Dictionary
```{r Full Dictionary}
# dictionary with 1 level (category)
df.dictApplied_Category <- mytoken %>% 
  tokens_lookup(dictionary = dict_CRPD,
                valuetype = "glob",
                levels = 1) %>% 
  dfm() %>%
  convert(to = "data.frame") %>% 
  # Merge geographic data
  left_join(select(CRPD_StateReports, doc_id, Region, SubRegion, RegionalGroup, OptionalProtocol, IncomeGroup),
            by = "doc_id") %>% 
  relocate(Region, SubRegion, RegionalGroup, OptionalProtocol, IncomeGroup, .after = doc_id) %>% 
  mutate(OptionalProtocol = as.factor(OptionalProtocol))

head(df.dictApplied_Category)

# dictionary with 2 levels (category and subcategory)
df.dictApplied_CatSubcategory <- mytoken %>% 
  tokens_lookup(dictionary = dict_CRPD,
                valuetype = "glob",
                levels = 1:2) %>% 
  dfm() %>%
  convert(to = "data.frame") %>% 
  # Merge geographic data
  left_join(select(CRPD_StateReports, doc_id, Region, SubRegion, RegionalGroup, OptionalProtocol, IncomeGroup),
            by = "doc_id") %>% 
  relocate(Region, SubRegion, RegionalGroup, OptionalProtocol, IncomeGroup, .after = doc_id) %>% 
  mutate(OptionalProtocol = as.factor(OptionalProtocol))

head(df.dictApplied_CatSubcategory)
```



```{r Full Dictionary - Category Plot, fig.height=2.5}
# Category Plot
df.dictApplied_Category %>% 
  select(-c(doc_id, Region, SubRegion, RegionalGroup)) %>% 
  pivot_longer(everything(), names_to = "Category", values_to = "count") %>% # transpose columns to rows
  plyr::ddply("Category", plyr::colwise(sum)) %>% # aggregate counts by category
  mutate(prop = round(count/sum(count), 4)) %>%
  slice_max(prop, n = 25) %>%
  ggplot(aes(x=reorder(toupper(Category), prop), 
             y=prop)) +
  geom_col(alpha = 1, show.legend = FALSE, fill = "#4472C4") +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10)),
                     labels = scales::percent) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank())

ggsave("CRPD_Data/Assets/dict_Category.jpg")
```

```{r Full Dictionary - Category Plot - Least Represented, fig.height=2.5}
# Category Plot
df.dictApplied_Category %>% 
  select(-c(doc_id, Region, SubRegion, RegionalGroup)) %>% 
  pivot_longer(everything(), names_to = "Category", values_to = "count") %>% # transpose columns to rows
  plyr::ddply("Category", plyr::colwise(sum)) %>% # aggregate counts by category
  mutate(prop = round(count/sum(count), 4)) %>%
  slice_min(prop, n = 25) %>%
  ggplot(aes(x=reorder(toupper(Category), -prop), 
             y=prop)) +
  geom_col(alpha = 1, show.legend = FALSE, fill = "#4472C4") +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10)),
                     labels = scales::percent) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank())

ggsave("CRPD_Data/Assets/dict_Category_Least.jpg")
```



```{r Full Dictionary - Category-Subcategory Plot, fig.height=2.5}
# Category-Subcategory Plot
df.dictApplied_CatSubcategory %>% 
  select(-c(doc_id, Region, SubRegion, RegionalGroup)) %>% 
  pivot_longer(everything(), names_to = "CatSubcategory", values_to = "count") %>% # transpose columns to rows
  plyr::ddply("CatSubcategory", plyr::colwise(sum)) %>% # aggregate counts by category
  mutate(prop = round(count/sum(count), 4)) %>%
  slice_max(prop, n = 25) %>% 
  ggplot(aes(x=reorder(toupper(CatSubcategory), prop), 
             y=prop)) +
  geom_col(alpha = 1, show.legend = FALSE, fill = "#4472C4") +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10)),
                     labels = scales::percent) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank())

ggsave("CRPD_Data/Assets/dict_SubCategory.jpg")
```



#### Keyword-In-Context (KWIC)
Use this section to investigate words driving dictionary categorization.
```{r KWIC by Category}
# see keywords-in-context for dictionary entries

# search by words in category
kwic(mytoken, pattern = phrase(dict_CRPD$Article_1)) %>% 
  as_data_frame() %>% 
  head(1000)

# search by words in subcategory
kwic(mytoken, pattern = phrase(dict_CRPD$Article_9$Paragraph_1b)) %>% 
  as_data_frame() %>% 
  head(1000)
```


```{r KWIC by Word}
# search by specific word
kwic(mytoken, pattern = phrase("mental integrity"), window = 10) %>% 
  as_data_frame() %>% 
  select(-c(from, to, pattern)) %>% 
  head(1000)
```


#### Categorical Breakdown
##### Category
###### Region
```{r Plot - By Region, fig.height=2.5}
df.dictApplied_Category %>% 
  select(-c(doc_id, SubRegion, RegionalGroup)) %>% 
  filter(!is.na(Region)) %>%
  # transpose columns to rows
  pivot_longer(cols = !Region,
               names_to = "Category",
               values_to = "Count") %>% 
  plyr::ddply(c("Region", "Category"), plyr::colwise(sum)) %>%   # aggregate counts by Region & Category
  group_by(Region) %>% 
  mutate(prop = round(Count/sum(Count), 4)) %>%
  slice_max(prop, n = 10) %>% 
  ungroup() %>% 
  mutate(Region = as.factor(Region)) %>% 
  ggplot(aes(x = reorder_within(Category, prop, Region), y = prop, 
           fill = Region)) +
  geom_col(alpha = 1, show.legend = FALSE) +
  # specify colours by fill (in this case, fill = Region so colours specified by Region)
  scale_fill_manual(values = c("#F8766D", "#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")) +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10))) +
  facet_wrap(~toupper(Region), scales = "free", ncol = 2) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
        strip.text = element_text(face = "bold"))

ggsave("CRPD_Data/Assets/dict_Category_AllRegions.jpg")
```


```{r Plot - By Region - Least Represented, fig.height=2.5}
df.dictApplied_Category %>% 
  select(-c(doc_id, SubRegion, RegionalGroup)) %>% 
  filter(!is.na(Region)) %>%
  # transpose columns to rows
  pivot_longer(cols = !Region,
               names_to = "Category",
               values_to = "Count") %>% 
  plyr::ddply(c("Region", "Category"), plyr::colwise(sum)) %>%   # aggregate counts by Region & Category
  group_by(Region) %>% 
  mutate(prop = round(Count/sum(Count), 4)) %>%
  slice_min(prop, n = 10) %>% 
  ungroup() %>% 
  mutate(Region = as.factor(Region)) %>% 
  ggplot(aes(x = reorder_within(Category, -prop, Region), y = prop, 
           fill = Region)) +
  geom_col(alpha = 1, show.legend = FALSE) +
  # specify colours by fill (in this case, fill = Region so colours specified by Region)
  scale_fill_manual(values = c("#F8766D", "#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")) +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10))) +
  facet_wrap(~toupper(Region), scales = "free", ncol = 2) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
        strip.text = element_text(face = "bold"))

ggsave("CRPD_Data/Assets/dict_Category_AllRegions_Least.jpg")
```


###### Sub-Region
```{r Plot - By SubRegion - Africa, fig.width=3.5}
df.dictApplied_Category %>% 
  filter(!is.na(SubRegion)) %>%
  filter(Region == "Africa") %>% 
  select(-c(doc_id, Region, RegionalGroup)) %>% 
  # transpose columns to rows
  pivot_longer(cols = !SubRegion,
               names_to = "Category",
               values_to = "Count") %>% 
  plyr::ddply(c("SubRegion", "Category"), plyr::colwise(sum)) %>%  # aggregate counts by SubRegion & Category
  group_by(SubRegion) %>% 
  mutate(prop = round(Count/sum(Count), 4)) %>%
  slice_max(prop, n = 10) %>% 
  ungroup() %>% 
  mutate(SubRegion = as.factor(SubRegion)) %>% 
  ggplot(aes(x = reorder_within(Category, prop, SubRegion), y = prop)) +
  geom_col(alpha = 1, show.legend = FALSE, fill = "#F8766D") +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.13))) +
  facet_wrap(~toupper(SubRegion), scales = "free", ncol = 2) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
        strip.text = element_text(face = "bold"))

ggsave("CRPD_Data/Assets/dict_Category_Africa.jpg")
```


```{r Plot - By SubRegion - Americas, fig.width=3.5}
df.dictApplied_Category %>% 
  filter(!is.na(SubRegion)) %>%
  filter(Region == "Americas") %>% 
  select(-c(doc_id, Region, RegionalGroup)) %>% 
  # transpose columns to rows
  pivot_longer(cols = !SubRegion,
               names_to = "Category",
               values_to = "Count") %>% 
  plyr::ddply(c("SubRegion", "Category"), plyr::colwise(sum)) %>%  # aggregate counts by SubRegion & Category
  group_by(SubRegion) %>% 
  mutate(prop = round(Count/sum(Count), 4)) %>%
  slice_max(prop, n = 10) %>% 
  ungroup() %>% 
  mutate(SubRegion = as.factor(SubRegion)) %>% 
  ggplot(aes(x = reorder_within(Category, prop, SubRegion), y = prop)) +
  geom_col(alpha = 1, show.legend = FALSE, fill = "#A3A500") +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.13))) +
  facet_wrap(~toupper(SubRegion), scales = "free", ncol = 2) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
        strip.text = element_text(face = "bold"))

ggsave("CRPD_Data/Assets/dict_Category_Americas.jpg")
```


```{r Plot - By SubRegion - Asia, fig.height=2.5, fig.width=3.5}
df.dictApplied_Category %>% 
  filter(!is.na(SubRegion)) %>%
  filter(Region == "Asia") %>% 
  select(-c(doc_id, Region, RegionalGroup)) %>% 
  # transpose columns to rows
  pivot_longer(cols = !SubRegion,
               names_to = "Category",
               values_to = "Count") %>% 
  plyr::ddply(c("SubRegion", "Category"), plyr::colwise(sum)) %>%  # aggregate counts by SubRegion & Category
  group_by(SubRegion) %>% 
  mutate(prop = round(Count/sum(Count), 4)) %>%
  slice_max(prop, n = 10) %>% 
  ungroup() %>% 
  mutate(SubRegion = as.factor(SubRegion)) %>% 
  ggplot(aes(x = reorder_within(Category, prop, SubRegion), y = prop)) +
  geom_col(alpha = 1, show.legend = FALSE, fill = "#00BF7D") +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.13))) +
  facet_wrap(~toupper(SubRegion), scales = "free", ncol = 2) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
        strip.text = element_text(face = "bold"))

ggsave("CRPD_Data/Assets/dict_Category_Asia.jpg")
```


```{r Plot - By SubRegion - Europe, fig.width=3.5}
df.dictApplied_Category %>% 
  filter(!is.na(SubRegion)) %>%
  filter(Region == "Europe") %>% 
  select(-c(doc_id, Region, RegionalGroup)) %>% 
  # transpose columns to rows
  pivot_longer(cols = !SubRegion,
               names_to = "Category",
               values_to = "Count") %>% 
  plyr::ddply(c("SubRegion", "Category"), plyr::colwise(sum)) %>%  # aggregate counts by SubRegion & Category
  group_by(SubRegion) %>% 
  mutate(prop = round(Count/sum(Count), 4)) %>%
  slice_max(prop, n = 10) %>% 
  ungroup() %>% 
  mutate(SubRegion = as.factor(SubRegion)) %>% 
  ggplot(aes(x = reorder_within(Category, prop, SubRegion), y = prop)) +
  geom_col(alpha = 1, show.legend = FALSE, fill = "#00B0F6") +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.13))) +
  facet_wrap(~toupper(SubRegion), scales = "free", ncol = 2) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
        strip.text = element_text(face = "bold"))

ggsave("CRPD_Data/Assets/dict_Category_Europe.jpg")
```


```{r Plot - By SubRegion - Oceania, fig.width=3.5}
df.dictApplied_Category %>% 
  filter(!is.na(SubRegion)) %>%
  filter(Region == "Oceania") %>% 
  select(-c(doc_id, Region, RegionalGroup)) %>% 
  # transpose columns to rows
  pivot_longer(cols = !SubRegion,
               names_to = "Category",
               values_to = "Count") %>% 
  plyr::ddply(c("SubRegion", "Category"), plyr::colwise(sum)) %>%  # aggregate counts by SubRegion & Category
  group_by(SubRegion) %>% 
  mutate(prop = round(Count/sum(Count), 4)) %>%
  slice_max(prop, n = 10) %>% 
  ungroup() %>% 
  mutate(SubRegion = as.factor(SubRegion)) %>% 
  ggplot(aes(x = reorder_within(Category, prop, SubRegion), y = prop)) +
  geom_col(alpha = 1, show.legend = FALSE, fill = "#E76BF3") +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.13))) +
  facet_wrap(~toupper(SubRegion), scales = "free", ncol = 2) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
        strip.text = element_text(face = "bold"))

ggsave("CRPD_Data/Assets/dict_Category_Oceania.jpg")
```


###### Optional Protocol
```{r Plot - By OptionalProtocol, fig.height=2.5}
df.dictApplied_Category %>% 
  select(-c(doc_id, Region, SubRegion, RegionalGroup)) %>% 
  filter(!is.na(OptionalProtocol)) %>%
  # transpose columns to rows
  pivot_longer(cols = !OptionalProtocol,
               names_to = "Category",
               values_to = "Count") %>% 
  plyr::ddply(c("OptionalProtocol", "Category"), plyr::colwise(sum)) %>%   # aggregate counts by OptionalProtocol & Category
  group_by(OptionalProtocol) %>% 
  mutate(prop = round(Count/sum(Count), 4)) %>%
  slice_max(prop, n = 10) %>% 
  ungroup() %>% 
  mutate(OptionalProtocol = as.factor(if_else(OptionalProtocol == 1,
                                              "Ratified",
                                              "Not Ratified"))) %>% 
  ggplot(aes(x = reorder_within(Category, prop, OptionalProtocol), y = prop, 
             fill = OptionalProtocol)) +
  geom_col(alpha = 1, show.legend = FALSE) +
  # scale_fill_manual(values = c("#F8766D", "#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")) +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10))) +
  facet_wrap(~toupper(OptionalProtocol), scales = "free", ncol = 2) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
        strip.text = element_text(face = "bold"))

ggsave("CRPD_Data/Assets/dict_Category_OptionalProtocol.jpg")
```


###### Income Level
```{r Plot - By Income Level, fig.height=2.5}
df.dictApplied_Category %>% 
  select(-c(doc_id, Region, SubRegion, RegionalGroup, OptionalProtocol)) %>% 
  filter(!is.na(IncomeGroup)) %>%
  # transpose columns to rows
  pivot_longer(cols = !IncomeGroup,
               names_to = "Category",
               values_to = "Count") %>% 
  plyr::ddply(c("IncomeGroup", "Category"), plyr::colwise(sum)) %>%   # aggregate counts by IncomeGroup & Category
  group_by(IncomeGroup) %>% 
  mutate(prop = round(Count/sum(Count), 4)) %>%
  slice_max(prop, n = 10) %>% 
  ungroup() %>% 
  mutate(IncomeGroup = as.factor(IncomeGroup)) %>% 
  ggplot(aes(x = reorder_within(Category, prop, IncomeGroup), y = prop, 
             fill = IncomeGroup)) +
  geom_col(alpha = 1, show.legend = FALSE) +
  # specify colours by fill (in this case, fill = IncomeGroup so colours specified by IncomeGroup)
  scale_fill_manual(values = c("#00BF7D", "#F8766D", "#E76BF3", "#00B0F6", "#A3A500")) +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10))) +
  facet_wrap(~toupper(IncomeGroup), scales = "free", ncol = 2) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
        strip.text = element_text(face = "bold"))

ggsave("CRPD_Data/Assets/dict_Category_IncomeGroups.jpg")
```


```{r Plot - By Income Level - Least Represented, fig.height=2.5}
df.dictApplied_Category %>% 
  select(-c(doc_id, Region, SubRegion, RegionalGroup, OptionalProtocol)) %>% 
  filter(!is.na(IncomeGroup)) %>%
  # transpose columns to rows
  pivot_longer(cols = !IncomeGroup,
               names_to = "Category",
               values_to = "Count") %>% 
  plyr::ddply(c("IncomeGroup", "Category"), plyr::colwise(sum)) %>%   # aggregate counts by IncomeGroup & Category
  group_by(IncomeGroup) %>% 
  mutate(prop = round(Count/sum(Count), 4)) %>%
  slice_min(prop, n = 10) %>% 
  ungroup() %>% 
  mutate(IncomeGroup = as.factor(IncomeGroup)) %>% 
  ggplot(aes(x = reorder_within(Category, -prop, IncomeGroup), y = prop, 
             fill = IncomeGroup)) +
  geom_col(alpha = 1, show.legend = FALSE) +
  # specify colours by fill (in this case, fill = IncomeGroup so colours specified by IncomeGroup)
  scale_fill_manual(values = c("#00BF7D", "#F8766D", "#E76BF3", "#00B0F6", "#A3A500")) +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10))) +
  facet_wrap(~toupper(IncomeGroup), scales = "free", ncol = 2) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
        strip.text = element_text(face = "bold"))

ggsave("CRPD_Data/Assets/dict_Category_IncomeGroups_Least.jpg")
```


## Dictionary: Disability Models
```{r Import Dictionary}
dict_DisabilityModels <- readRDS("CRPD_Data/Dictionary/dict_DisabilityModels_Final.rds")
```


### Apply Dictionary
```{r Full Dictionary}
# dictionary with 1 level (category)
df.dictDisabilityModels_Applied <- mytoken %>% 
  tokens_lookup(dictionary = dict_DisabilityModels,
                valuetype = "glob",
                levels = 1) %>% 
  dfm() %>%
  convert(to = "data.frame") %>% 
  # Merge geographic data
  left_join(select(CRPD_StateReports, doc_id, Region, SubRegion, RegionalGroup),
            by = "doc_id") %>% 
  relocate(Region, SubRegion, RegionalGroup, .after = doc_id)

head(df.dictDisabilityModels_Applied)
```


```{r Disability Model - Category Plot}
df.dictDisabilityModels_Applied %>% 
  select(-c(doc_id, Region, SubRegion, RegionalGroup)) %>% 
  pivot_longer(everything(), names_to = "Category", values_to = "count") %>% # transpose columns to rows
  plyr::ddply("Category", plyr::colwise(sum)) %>% # aggregate counts by category
  mutate(prop = round(count/sum(count), 4)) %>%
  ggplot(aes(x=reorder(toupper(Category), prop), 
             y=prop)) +
  geom_col(alpha = 1, show.legend = FALSE, fill = "#4472C4") +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.10)),
                     labels = scales::percent) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank())

ggsave("CRPD_Data/Assets/dict_DisabilityModels_Global.jpg")
```


```{r Disability Model - Plot - By Region, fig.height=2.5}
df.dictDisabilityModels_Applied %>% 
  select(-c(doc_id, SubRegion, RegionalGroup)) %>% 
  filter(!is.na(Region)) %>%
  # transpose columns to rows
  pivot_longer(cols = !Region,
               names_to = "Category",
               values_to = "Count") %>% 
  plyr::ddply(c("Region", "Category"), plyr::colwise(sum)) %>%   # aggregate counts by Region & Category
  group_by(Region) %>% 
  mutate(prop = round(Count/sum(Count), 4)) %>%
  ungroup() %>% 
  mutate(Region = as.factor(Region)) %>% 
  ggplot(aes(x = reorder_within(toupper(Category), prop, Region), y = prop, 
             fill = Region)) +
  geom_col(alpha = 1, show.legend = FALSE) +
  # specify colours by fill (in this case, fill = Region so colours specified by Region)
  scale_fill_manual(values = c("#F8766D", "#A3A500", "#00BF7D", "#00B0F6", "#E76BF3")) +
  coord_flip() +
  geom_text(aes(label = scales::percent(prop, accuracy = 0.01)),
            size = 3,
            vjust = 0.5,
            hjust = -0.2) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.12))) +
  facet_wrap(~toupper(Region), scales = "free", ncol = 2) +
  scale_x_reordered() +
  labs(x = NULL,
       y = NULL) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank(),
        strip.text = element_text(face = "bold"))

ggsave("CRPD_Data/Assets/dict_DisabilityModels_AllRegions.jpg")
```


#### Keyword-In-Context (KWIC)
Use this section to investigate words driving dictionary categorization.
```{r KWIC by Category}
# see keywords-in-context for dictionary entries

# search by words in category
kwic(mytoken, pattern = phrase(dict_DisabilityModels$Rights_Model)) %>% 
  as_data_frame() %>% 
  head(1000)
```


```{r KWIC by Word}
# search by specific word
kwic(mytoken, pattern = phrase("inclusive society"), window = 10) %>% 
  as_data_frame() %>% 
  select(-c(from, to, pattern)) %>% 
  head(1000)
```

